Job Demands-Resources model components through the lens of O*NET classifications

### 2023-01-31 Submission.tex
tuesday edits

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Job Demands-Resources model components through the lens of O*NET classifications},
  pdfauthor={Alicia Stachowski1, John Kulas2, \& Renata Garcia Prieto Palacios Roji3},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

@@

Lastly, we propose three research that explicitly address a topic hinted at in the literature review above. Although challenge stressors tend to be appraised more so as challenges, and hindrance stressors tend to be appraised more as hindrances than challenges, there remains variability in these appraisals (M. A. LePine, 2022). M. A. LePine (2022), in fact, argues that the challenge-hindrance stressor framework acknowledges that these appraisals are not universal. We explore whether literature-implicated job characteristics (e.g., autonomy) are consistently rated as our research models suggest across the job-demands resources theory (Bakker \& Demerouti, 2017)and challenge-hindrance stressor framework (Cavanaugh et al., 2000).

@@

\begin{quote}
\emph{Research Question 2}: Are literature-implicated challenges consistently rated as job challenges?
\end{quote}

\begin{quote}
\emph{Research Question 3}: Are literature-implicated hiderances consistently rated as job hindrances?
\end{quote}

@@

Of the 785 Prolific panel individuals who initially accessed the survey link, 112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (Yentes \& Wilhelm, 2021). Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of 568 respondents who constitute the current sample. Regarding tenure, 13.57\% had been in their referent job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years. Respondent ages ranged from 18 to 65 with an average of 28.18 years old (\emph{SD} = 7.53). The survey offered a free-field gender identity category, although the sample predominantly self-identified as female (52.58\%) or male (46.83\%).

@@

Our survey was informed by 98 statements taken from job characteristic descriptors located within O*Net's classification of ``work activities'': 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and ``work context'' groupings: 1) Interpersonal Relationships (14 statements), 2) Physical Work Conditions (30 statements), and 3) Structural Job Characteristics (13 statements).

The O*Net descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to ``responsibility'' than task. For example, the descriptor for ``level of competition'', which is an element of the ``structural job characteristics'' grouping, is \emph{\ldots to what extent does this job require the worker to compete or to be aware of competitive pressures?} Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we retained the O*Net wording for our item stems. We also retained O*Net's response scales, several of which were semantically unique across items, but all shared the same 5-point scale. It would likely NOT be considered controversial to referred to these as ``effectively'' Likert-type response scales.

@@

These descriptors often have \href{https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2}{unique response categories}. For example, the statement ``How responsible is the worker for work outcomes and results of other workers?'' has response options ranging from \emph{No responsibility} to \emph{Very high responsibility}, while the statement, ``How often do you use electronic mail in this job?'' has options ranging from \emph{Never} to \emph{Every day}. We retained the essence of each O*NET descriptor to capture characteristics of relevance for each respondent. Subsequent to these self evaluations, each respondent who agreed that the element had \emph{at least some relevance} to their job was also asked to rate that element in terms of, 1) \ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) \ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) \ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.

@@

Outline:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Hypothesis 1: Job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource.
\end{enumerate}

\begin{quote}
Done - Figure \ref{fig:overallhist}
\end{quote}

\begin{quote}
NOT DONE: Combine current graphs 2 \(\rightarrow\) 8 into only 2 graphs (put resources, challenges, and demands on same graph; Kulas do this)
\end{quote}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  Hypothesis 2: Job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand.
\end{enumerate}

\begin{quote}
Done (at O*Net dimension level) - Table \ref{tab:cortab}.
\end{quote}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\item
  \emph{Research Question 1}: Are literature-implicated resources consistently rated as job resources?
\item
  \emph{Research Question 2}: Are literature-implicated challenges consistently rated as job challenges?
\item
  \emph{Research Question 3}: Are literature-implicated hindrances consistently rated as job hindrances?
\end{enumerate}

\begin{quote}
Alicia can you present ``what this means'' and what is being presented in Figure \ref{fig:scalelevelgraphs} more clearly - also possibly add ANOVAs
\end{quote}

@@

Figure \ref{fig:overallhist} presents standard deviations of characteristic perceptions, grouped by whether that characteristic was rated as a resource, challenge, or demand. As can be seen in the figure, there was a wide range of agreement versus disagreement with resources and challenges, but hindrances were almost universally associated with disagreement (Bartlett's \(K^2\) = 76.83, \emph{p} = 0.00 ).

@@

Figure \ref{fig:combinegraphs} presents resources, challenges, and hindrances that are \emph{largely agreed on} as indexed by (relatively) low standard deviations.\footnote{There were a few characteristics with standard deviations of ``zero'' but these were excluded from presenation as they were likely representing only one person (\emph{n}'s should also go on these graphs if they're retained - Alicia's idea 12/2 was to use initial ratings as indicators of counts).} There are only 8 characteristics presented per perceived category because of limited space. All sortable ratings are available in the online resources.

@@

Figure \ref{fig:combinegraphs2} presents the resources, challenges, and hindrances that are \emph{largely disagreed on} as indexed by (relatively) high standard deviations (these are the 8 characteristics with the greatest variability in rating).

@@

@@

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Job Demands-Resources model components through the lens of O*NET classifications},
  pdfauthor={Alicia Stachowski1, John Kulas2, \& Renata Garcia Prieto Palacios Roji3},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

Lastly, we propose three research questions that explicitly address a topic discussed above. Although challenge stressors tend to be appraised more so as challenges, and hindrance stressors tend to be appraised more as hindrances than challenges, there remains variability in these appraisals (M. A. LePine, 2022). M. A. LePine (2022), in fact, argues that the challenge-hindrance stressor framework acknowledges that these appraisals are not universal. We explore whether literature-implicated job characteristics (e.g., autonomy) are consistently rated as our research models suggest across the job-demands resources theory (Bakker \& Demerouti, 2017) and challenge-hindrance stressor framework (Cavanaugh et al., 2000).

@@

\begin{quote}
\emph{Research Question 2}: Are literature-implicated demands consistently rated as job demands?
\end{quote}

@@

Of the 785 individuals who initially accessed the survey link, 112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (Yentes \& Wilhelm, 2021). Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of 568 respondents who constitute the current sample. Regarding tenure, 13.57\% had been in their referent job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years. Respondent ages ranged from 18 to 65 with an average of 28.18 years old (\emph{SD} = 7.53). The survey offered a free-field gender identity category, although the sample predominantly self-identified as female (52.58\%) or male (46.83\%).

@@

These descriptors often have \href{https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2}{unique response categories}. For example, the statement ``How responsible is the worker for work outcomes and results of other workers?'' has response options ranging from \emph{No responsibility} to \emph{Very high responsibility}, while the statement, ``How often do you use electronic mail in this job?'' has options ranging from \emph{Never} to \emph{Every day}. The O*Net descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to ``responsibility'' than task. For example, the descriptor for ``level of competition'', which is an element of the ``structural job characteristics'' grouping, is \emph{\ldots to what extent does this job require the worker to compete or to be aware of competitive pressures?} Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we retained the O*Net wording for our item stems. We also retained O*Net's response scales, several of which were semantically unique across items, but all shared the same 5-point scale. It would likely NOT be considered controversial to referred to these as ``effectively'' Likert-type response scales.

We retained the essence of each O*NET descriptor to capture characteristics of relevance for each respondent. Subsequent to these self evaluations, each respondent who agreed that the element had \emph{at least some relevance} to their job was also asked to rate that element in terms of, 1) \ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) \ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) \ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.

@@

@@

@@

The first prediction asks whether job characteristics differ in variability/stability regarding
subjective worker perception as a demand or resource. Figure \ref{fig:overallhist} presents standard deviations of characteristic perceptions, grouped by whether that characteristic was rated as a resource, challenge, or demand. As can be seen in the figure, there was a wide range of agreement versus disagreement with resources and challenges, but hindrances were almost universally associated with disagreement (Bartlett's \(K^2\) = 76.83, \emph{p} = 0.00 ).

@@

Figure \ref{fig:combinegraphs} presents resources, challenges, and hindrances that are \emph{largely agreed on} as indexed by (relatively) low standard deviations.\footnote{There were a few characteristics with standard deviations of ``zero'' but these were excluded from presentation as they were likely representing only one person (\emph{n}'s should also go on these graphs if they're retained - Alicia's idea 12/2 was to use initial ratings as indicators of counts).} There are only 8 characteristics presented per perceived category because of limited space. All sortable ratings are available in the online resources.

@@

Figure \ref{fig:combinegraphs2} presents the resources, challenges, and hindrances that are \emph{largely disagreed on} as indexed by (relatively) high standard deviations (these are the 8 characteristics with the greatest variability in rating). In sum, these results provide some support for H1, particularly for hindrances, which are consistently viewed as ``different''.

@@

Figure 4 highs the average characteristic rating grouped by the literature implicated categories shown on the right. These categories are frequently presented in descriptions of the JD-R model and theory (cite). To answer these research questions, authors categorized items into the categories listed in the literature. For example, autonomy is frequently described as a resource. An O*Net item in the ``autonomy'' category is ``How much decision making freedom, without supervision, does your job offer?''. Means for respondent-rated resources, challenges, and hindrances were then computed to explore whether literature-implicated resources and demands were consistently rated as such. The left side of Figure 8 shows literature-derived demands (e.g., work pressure). We do not see a clear pattern of high ratings as hindrances for these demands. In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much more variability in how employees rated what should objectively be ``hindrances'' at work. However, in contrast, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings. Here, the white bars representing resources are consistently higher. ADD ANOVAS HERE - one way repeated measures for each category (total of 10 analyses). describe pattern. In sum, these results provide \_\_\_ support for RQ 1 and 2.

challenges

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(tidyr)}

\NormalTok{foranova }\OtherTok{\textless{}{-}}\NormalTok{ data}
\NormalTok{foranova}\SpecialCharTok{$}\NormalTok{subject }\OtherTok{\textless{}{-}} \DecValTok{1}\SpecialCharTok{:}\FunctionTok{nrow}\NormalTok{(foranova) }

\NormalTok{anova1 }\OtherTok{\textless{}{-}} \FunctionTok{gather}\NormalTok{(foranova,type,score,resources\_workpressure}\SpecialCharTok{:}\NormalTok{hindrance\_autonomy, }\AttributeTok{factor\_key=}\ConstantTok{TRUE}\NormalTok{)}

\DocumentationTok{\#\# now need to isolate rows with targeted characteristics}

\NormalTok{overwork }\OtherTok{\textless{}{-}}\NormalTok{ anova1[ }\FunctionTok{which}\NormalTok{(anova1}\SpecialCharTok{$}\NormalTok{type}\SpecialCharTok{==}\StringTok{\textquotesingle{}resources\_phyworkload\_wkover\textquotesingle{}} \SpecialCharTok{|}\NormalTok{ anova1}\SpecialCharTok{$}\NormalTok{type}\SpecialCharTok{==}\StringTok{\textquotesingle{}challenge\_phyworkload\_wkover\textquotesingle{}} \SpecialCharTok{|}\NormalTok{ anova1}\SpecialCharTok{$}\NormalTok{type}\SpecialCharTok{==}\StringTok{\textquotesingle{}hindrance\_phyworkload\_wkover\textquotesingle{}}\NormalTok{), ]}

\NormalTok{rstatix}\SpecialCharTok{::}\FunctionTok{anova\_test}\NormalTok{(}\AttributeTok{data=}\NormalTok{overwork,}\AttributeTok{dv=}\NormalTok{score,}\AttributeTok{wid=}\NormalTok{subject,}\AttributeTok{within=}\NormalTok{type) }
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## ANOVA Table (type III tests)
## 
## $ANOVA
##   Effect DFn  DFd      F        p p<.05   ges
## 1   type   2 1134 17.709 2.67e-08     * 0.017
## 
## $`Mauchly's Test for Sphericity`
##   Effect     W        p p<.05
## 1   type 0.694 1.29e-45     *
## 
## $`Sphericity Corrections`
##   Effect   GGe       DF[GG]    p[GG] p[GG]<.05   HFe      DF[HF]    p[HF]
## 1   type 0.766 1.53, 868.32 7.09e-07         * 0.767 1.53, 870.2 6.93e-07
##   p[HF]<.05
## 1         *
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{trying }\OtherTok{\textless{}{-}} \FunctionTok{aov}\NormalTok{(}\AttributeTok{formula =}\NormalTok{ score }\SpecialCharTok{\textasciitilde{}}\NormalTok{ type }\SpecialCharTok{+} \FunctionTok{Error}\NormalTok{(subject}\SpecialCharTok{/}\NormalTok{type), }\AttributeTok{data=}\NormalTok{overwork)}
\FunctionTok{summary}\NormalTok{(trying)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Error: subject
##           Df Sum Sq Mean Sq F value Pr(>F)
## Residuals  1  8.266   8.266               
## 
## Error: subject:type
##      Df Sum Sq Mean Sq
## type  2  15.04   7.519
## 
## Error: Within
##             Df Sum Sq Mean Sq F value  Pr(>F)   
## type         2    9.2   4.586   5.989 0.00256 **
## Residuals 1698 1300.2   0.766                   
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\DocumentationTok{\#\# pairwise\_t\_test( value\textasciitilde{}time,paired=TRUE, p.adjust.method = "bonferroni" ) }

\CommentTok{\# check \textless{}{-} overwork[,c(406:407)]}
\CommentTok{\# psych::describe.by(check, group=check$type)}
\end{Highlighting}
\end{Shaded}

@@

NOTE: Add a table of the items (probably the full list and those we included in challenge, hindrance specifically). Could also have a column showing which items were used for Figure 4 categories.
Summary
The major aim and contribution of this paper was to examine whether there was variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and also whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics using a sample of items from O*Net. The findings broadly revealed that there was relatively more consistency in ratings resources and challenges characteristics, and far more variability in job characteristics rated as hindrance stressors. This finding lends additional evidence to Horan et al.'s (2020) conclusion that ``\ldots stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees'' (p.~3). The research questions regarding the match between literature-implicated demand and resource categories and empirical ratings aligns with the consistency/variability we observed in H1. Interestingly, we consistently observed that job characteristics rated as resources were also rated highly as challenge stressors, which are not inherently negative in the way that hindrance stressors are. Lastly, we also found support for the prediction that job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand.
Practical Implications
The reality that there is more individual difference in what employees perceive to be a hindrance and less in what is perceived to be a resource or challenge stressor is in some ways encouraging. These findings provide comforting support for the idea that managers and supervisors can predict which characteristics are perceived as supportive to employees' performance. Somewhat surprisingly, hindrances are rated more variably. As such, one important implication is that of frequent communication with employees regarding their perceptions of characteristics that limit their performance. ADD MORE
Limitations and Future Directions
• Captured only a small number of job characteristics
• Part of that means we captured minimal ``social'' resources or interactions with one's supervisor
• Should expand on the kinds of resources employees experience, as well as stressors
• Definition of resource, challenge, hindrance -- question of distinction between resource and challenge (think about this one a little bit)

Conclusion
In sum, this endeavor explored the job-demands-resources literature from a unique lens, showing that there are far more individual differences in how employees perceive demands and resources than much of our current research suggests. While resources and challenges are more similarly experienced, hindrance demands show a wide amount of variability.
